\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
Updated environment details to conda

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{venv}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}

>>>>

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{Conda Enviroment}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}
